Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-12-26 examples.tex
find the mistake

    Now let's see what we get when we invert $t$ and $t-s$ respectively. First let's find $ L_s = L\otimes\CC\xt$. 
    \[
        L_s  = \CC[t]\langle(t-s) e_1 - be_2 - ce_3 , (t-s) e_2 , e_3 \rangle = \CC[t]\langle(t-s) e_1 - be_2, (t-s) e_2, e_3 \rangle
    \]
    so 
    \[
    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[e_2]\}} = \begin{bmatrix}
        s \\
        -b & s 
    \end{bmatrix}
    \]
    which has block type $\mu_2$ and Jordan type $\lambda_2$ as expected.

    Next let's find $L_0 = L\otimes\CC\xt[t-s]$. 
    \[
        L_0 = \CC[t]\langle
        t^3 e_1 - bte_2 - ce_3, te_2 - de_3 , te_3 
        \rangle 
    \]
    so 
    \[
    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
        0 \\
        1 & 0 \\
        0 & 1 & 0 \\
          & & & 0 \\
          & & & d & 0  
    \end{bmatrix}
    \]
    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected!
\end{example}

>>>>

    Now let's see what we get when we invert $t$ and $t-s$ respectively.

    First let's invert $t$ by considering $L_2 = L\otimes\CC\xt[t-s]$. 
    \[
        L_2  = \CC[t,t^{-1}]\langle(t-s) e_1 -\frac{a+bt}{t^3} e_2 - \frac c {t^3} e_3, (t-s) e_2 - \frac d t e_3, e_3 \rangle
    \]
    so in $L_0/L_2$ we have 
    \[
    t[e_1] = s[e_1] + \frac{a+bt}{t^3} [e_2] + \frac c {t^3}  [e_3] \qquad t[e_2] = s[e_2] + \frac d t[e_3]    \qquad [e_3] = 0 
    \]
    and
    \[
    \left[t\big|_{L_0/L_2}\right]_{\{[e_1],[e_2]\}} = \begin{bmatrix}
        s \\
        \frac{a+bt}{t^3} & s 
    \end{bmatrix}
    \]
    which upon subtracting $s I$ gives a matrix having block type $\mu_2$ and Jordan type $\lambda_2 = (2)$ assuming $\frac{a+bt}{t^3}\ne 0$.

    Next let's invert $t-s$ by considering $L_1 = L\otimes\CC\xt$. 
    \[
        L_1 = \CC[t,(t-s)^{-1}]\langle
        t^3 e_1 - \frac{a+bt}{t-s}e_2 - \frac c {t-s} e_3, te_2 - \frac d {t-s} e_3 , te_3 
        \rangle 
    \]
    so in $L_0/L_1$ we have 
    \begin{align*}
        t[e_1] &= [te_1] \\
        t[te_1] &= [t^2 e_1] \\ 
        t[t^2e_1] & = \frac{a+bt}{t-s}[e_2] + \frac c {t-s} [e_3] \\
        t[e_2] &= \frac d {t-s} [e_3] \\ 
        t[e_3] &= 0 
    \end{align*}
    and 
    \[
    \left[t\big|_{L_0/L_1}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
        0 \\
        1 & 0 \\
        0 & 1 & 0 \\
          & & \frac{a+bt}{t-s} & 0 \\
          & & \frac c {t-s} & \frac d {t-s} & 0  
    \end{bmatrix}
    \]
    taking transpose 
    \[
        \begin{bmatrix}
            0 & 1\\
              & 0 & 1\\
              &   & 0 & \frac{a+bt}{t-s} & \frac c {t-s} \\
              & & & 0 & \frac d {t-s} \\
              & & & & 0  
        \end{bmatrix}
    \]
    which has block type $\mu_1$ and Jordan type $\lambda_1 = (3,2)$ assuming $\frac{a+bt}{t-s}=0$ and one of the entries in the last column is not zero!?

    We found $a = 0$ and $cs - bd = 0$ above. So actually $\frac{a+bt}{t^3} = \frac b{t^2} \ne 0$ and $\frac{a + bt}{t-s} = \frac{bt}{t-s}$...Roger find my mistake. 
\end{example}
